---
title: "Statistical Distrib 08.30.2018"
author: "Nina Dyatchenko"
date: "August 30, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Descrete Random Variables
We have a few common exampes of discrete random variables. Each distribution also has a corresponding implementation in 'R'.
1. The Bernoulli distribution <https://en.wikipedia.org/wiki/Bernoulli_distribution>. 

```{r}
# Random Bernoulli - only one trial (flipping a coin, ourcomes 1 or 0)

rbinom(n=1, size=1, prob= 0.5)

# Weighted coin 
rbinom(n=1, size=1, prob=0.75)
```

2. Binomial Distribution: 
```{r}

# Flip 10 coins and record the results
rbinom(n=10, size=1, prob=0.5)

# Flip 10 fair coind and record number of succeses
rbinom(n=1, size=10, prob=0.5)

```

3. Poisson Destribusion. People kicks with by a horseanad killed. <https://en.wikipedia.org/wiki/Poisson_distribution>

```{r}
# How many horse kicks in each group of 10 soldiers? We expect (lambda) 2 kicks. So 2 is a mean/expected.
rpois(n=10, lambda=2)

# No whte horses are angry. Now 4 kicks is a mean.
rpois(n=10, lambda=4)
```

## Moments of these Distrebutions. 
The comment Momemts are the first and second Moment, from which we calculte the mean and variance respectively. 

### Binomial
```{r}
# Random draw of 5 faiar coins
xBinom <- rbinom(n=5, size=1, prob=0.5)
xBinom

# Mean
mean(xBinom)

# variance
var(xBinom)

# Random draw of 100 faiar coins
xBinom2 <- rbinom(n=100, size=1, prob=0.5)
xBinom2

# Mean
mean(xBinom2)


# variance
var(xBinom2)
```



## Continuous Random Variables