---
title: "R Assignment 4"
author: "Nina Dyatchenko"
date: "September 12th, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Assignment 4: Due Sunday, 16 September at 23:59PM
*For help with Rmarkdown for reports, see this [white paper](http://www.stat.cmu.edu/~cshalizi/rmarkdown/#math-in-r-markdown) from Carnegie Mellon University's Department of Statistics and Data Science.*

For each the seven statistical distributions we covered in the last assignment (Normal, Student's $t$, $\chi ^ 2$, $F$, Binomial, Negative Binomial, and Poisson), 

1. Generate and store a random vector of 10,000 observations, using the same parameters as the last homework:
    i. $N(\mu = 2, \sigma ^ 2 = 5 )$,
    
```{r}
set.seed(1)
xNorm_n10000 <- rnorm(n=10000, mean=2, sd = sqrt(5))
```

    ii. $t_{\nu = 4}$,
```{r}
set.seed(2)
xrt_n10000 <- rt(n=10000, df=4)
```

    iii. $\chi^2_{\nu = 2}$,
```{r}
set.seed(3)
xChi_n10000<- rchisq(n=10000, df=2, ncp=0)
```

    iv. $F_{n = 90,\ m = 12}$,
```{r}
set.seed(4)
xFd_n10000<- rf(n=10000, df1=90, df2=12)
```

    v. $Bin(n = 9, p = 2/3)$,
```{r}
set.seed(5)
xBD_n10000 <- rbinom(n=10000, size=9, prob=2/3)
```

    vi. $NBin(n = 5, p = 1/2)$, and
```{r}
set.seed(6)
xNB_n10000 <- rnbinom(n = 10000, size = 5, prob = 0.5)
```

    vii. $Pois(\lambda = 3)$.
```{r}
set.seed(7)
xP_n10000 <- rpois(n=10000, 3)
```

2. Subset the first $N = 6$ values from the vector, and of this subset
    i. calculate the 5-Number Summary,
    ii. plot the histogram of the subset, and
    iii. plot the estimated density of this subset. (Density assumes as normal).

Normal:
```{r}
NormSubs6<- xNorm_n10000[1:6]
summary(NormSubs6)
hist(NormSubs6)
plot(density(NormSubs6))
```

Student's $t$:

```{r}
TSubs6<- xrt_n10000[1:6]
summary(TSubs6)
hist(TSubs6)
plot(density(TSubs6))
```

$\chi ^ 2$ (Not normal)
```{r}
ChiSubs6<- xChi_n10000[1:6]
summary(ChiSubs6)
hist(ChiSubs6)
plot(density(ChiSubs6))
```

$F$-Distribution

```{r}
FSubs6<- xFd_n10000[1:6]
summary(FSubs6)
hist(FSubs6)
plot(density(FSubs6))
```

Binomial

```{r}
BDSubs6<- xBD_n10000[1:6]
summary(BDSubs6)
hist(BDSubs6)
plot(density(BDSubs6))
```

Negative binomial

```{r}
NegSubs6<- xNB_n10000[1:6]
summary(NegSubs6)
hist(NegSubs6)
plot(density(NegSubs6))
```

Poisson

```{r}
PoisSubs6<- xP_n10000[1:6]
summary(PoisSubs6)
hist(PoisSubs6)
plot(density(PoisSubs6))
```


3. Repeat Item 2 for the first $N =  10,\ 20,\ 30,\ \text{and}\ 50$ values from the random vector you generated in Item 1. Remark on the changing behaviour as the sample size increases. 

Normal:
```{r}
NormSubs10<- xNorm_n10000[1:10]
summary(NormSubs10)
hist(NormSubs10)
plot(density(NormSubs10))

NormSubs20<- xNorm_n10000[1:20]
summary(NormSubs20)
hist(NormSubs20)
plot(density(NormSubs20))

NormSubs30<- xNorm_n10000[1:30]
summary(NormSubs30)
hist(NormSubs30)
plot(density(NormSubs30))

NormSubs50<- xNorm_n10000[1:50]
summary(NormSubs50)
hist(NormSubs50)
plot(density(NormSubs50))
```

Student's $t$:

```{r}
TSubs10<- xrt_n10000[1:10]
summary(TSubs10)
hist(TSubs10)
plot(density(TSubs10))
var(TSubs10)

TSubs20<- xrt_n10000[1:20]
summary(TSubs20)
hist(TSubs20)
plot(density(TSubs20))
var(TSubs20)


TSubs30<- xrt_n10000[1:30]
summary(TSubs30)
hist(TSubs30)
plot(density(TSubs30))
var(TSubs30)


TSubs50<- xrt_n10000[1:50]
summary(TSubs50)
hist(TSubs50)
plot(density(TSubs50))
var(TSubs50)
```

$\chi ^ 2$
```{r}
ChiSubs10<- xChi_n10000[1:10]
summary(ChiSubs10)
hist(ChiSubs10)
plot(density(ChiSubs10))
var(ChiSubs10)

ChiSubs20<- xChi_n10000[1:20]
summary(ChiSubs20)
hist(ChiSubs20)
plot(density(ChiSubs20))
var(ChiSubs20)

ChiSubs30<- xChi_n10000[1:30]
summary(ChiSubs30)
hist(ChiSubs30)
plot(density(ChiSubs30))
var(ChiSubs30)

ChiSubs50<- xChi_n10000[1:50]
summary(ChiSubs50)
hist(ChiSubs50)
plot(density(ChiSubs50))
var(ChiSubs50)
```


4. Repeat Item 2 for the entire vector ($N = 10000$). For smaller values of $N$ from continuous distributions, which tool do you think gave a better representation of the full data: histogram or density plot? Did this change when you inspected the discrete distributions?

Normal:
```{r}
summary(xNorm_n10000)
hist(xNorm_n10000)
plot(density(xNorm_n10000))
var(xNorm_n10000)
```

Student's $t$:

```{r}
summary(xrt_n10000)
hist(xrt_n10000)
plot(density(xrt_n10000))
```
5. Contrast the 5-Number Summaries at each of the sample sizes (6, 10, 20, 30, 50, and 10000) for the skewed distributions (Negative binomial, Chi^2, F)vs. the symmetric distributions (Binomial, T, Normal).

Normal:
```{r}
summary(NormSubs6)
summary(NormSubs10)
summary(NormSubs20)
summary(NormSubs30)
summary(NormSubs50)
summary(xNorm_n10000)
var(NormSubs6)
var(NormSubs10)
var(NormSubs30)
var(NormSubs50)
var(xNorm_n10000)
```
Binomial:```{r}
summary(BDSubs6)
summary(BDSubs10)
summary(BDSubs20)
summary(BDSubs30)
summary(BDSubs50)
summary(xBD_n10000)






