---
title: "Assingment 6"
author: "Nina Dyatchenko"
date: "September 28, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 6: Due Sunday, 30 September at 23:59PM
*For help with Rmarkdown for reports, see this [white paper](http://www.stat.cmu.edu/~cshalizi/rmarkdown/#math-in-r-markdown) from Carnegie Mellon University's Department of Statistics and Data Science.*

### Part 1
Finish the work you have left over from Assignment 5. Email me when you finish, so I can look at it. Please finish this by Tuesday evening.
**Done**

### Part 2
Read [this article](https://www.r-bloggers.com/5-ways-to-subset-a-data-frame-in-r/) and execute the code in it. For the last example in this article (using the `dplyr` package), use the `tidyverse` package you just installed instead. The `filter()` and `select()` functions are the same. Include the code from this article and your output as the first section of your markdown report.

```{r}
### import education expenditure data set and assign column names
education <- read.csv("https://vincentarelbundock.github.io/Rdatasets/csv/robustbase/education.csv", stringsAsFactors = FALSE)
colnames(education) <- c("X","State","Region","Urban.Population","Per.Capita.Income","Minor.Population","Education.Expenditures")
#View(education)
head(education)

ed_exp1 <- education[c(10:21),c(2,6:7)] # extracts observations from Region 2 (raws from 10 to 21) and three variables: State (column 2), Minor.Population (column 6), and Education.Expenditures (C0lumn 7)
ed_exp1

ed_exp2 <- education[-c(1:9,22:50),-c(1,3:5)] # will give same results as ed_exp1 by ommitting raws and colums that we don't need (using negative vector)
ed_exp2

ed_exp3 <- education[which(education$Region == 2),names(education) %in% c("State","Minor.Population","Education.Expenditures")]
# We retrieve the columns of the subset by using the %in% operator on the names of the education data frame.
ed_exp3

ed_exp4 <- subset(education, Region == 2, select = c("State","Minor.Population","Education.Expenditures"))
# The subset() function return subsets of vectors, matrices or data frames which meet conditions. Takes 3 arguments: the data frame you want subsetted, the rows corresponding to the condition by which you want it subsetted, and the columns you want returned. 
ed_exp4
```

For the last example in this article (using the `dplyr` package), use the `tidyverse` package you just installed instead. The `filter()` and `select()` functions are the same. Include the code from this article and your output as the first section of your markdown report.

```{r}
library(tidyverse)
ed_exp5 <- select(filter(education, Region == 2),c(State,Minor.Population:Education.Expenditures))
ed_exp5
```


### Part 3
1. Create the `myClass` data frame we covered in class. When you create the data frame, make sure that your character **strings** are not changed to **factors** (look at `?data.frame` for the `stringsAsFactors` argument; also look at how the article does it). Include a row in the data frame for me, you, and your classmates. Here are the features to measure:
    a. last name
    b. first name
    c. number of cups of coffee or tea per day, and
    d. current neighbourhood
2. For each of the five data-frame subsetting methods in the article above, subset
    i. Your row
    ii. the column of neighbourhoods
    iii. your current neighbourhood
    iv. your AND my current neighbourhood, as a data frame
    v. the rows with people who drink coffee or tea
    vi. the neighbourhoods of people who *do not* drink coffee or tea