---
title: "Assingment 6"
author: "Nina Dyatchenko"
date: "September 28, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 6: Due Sunday, 30 September at 23:59PM
*For help with Rmarkdown for reports, see this [white paper](http://www.stat.cmu.edu/~cshalizi/rmarkdown/#math-in-r-markdown) from Carnegie Mellon University's Department of Statistics and Data Science.*

### Part 1
Finish the work you have left over from Assignment 5. Email me when you finish, so I can look at it. Please finish this by Tuesday evening.
**Done**

### Part 2
Read [this article](https://www.r-bloggers.com/5-ways-to-subset-a-data-frame-in-r/) and execute the code in it. For the last example in this article (using the `dplyr` package), use the `tidyverse` package you just installed instead. The `filter()` and `select()` functions are the same. Include the code from this article and your output as the first section of your markdown report.

```{r}
### import education expenditure data set and assign column names
education <- read.csv("https://vincentarelbundock.github.io/Rdatasets/csv/robustbase/education.csv", stringsAsFactors = FALSE)
colnames(education) <- c("X","State","Region","Urban.Population","Per.Capita.Income","Minor.Population","Education.Expenditures")
#View(education)
head(education)

ed_exp1 <- education[c(10:21),c(2,6:7)] # extracts observations from Region 2 (raws from 10 to 21) and three variables: State (column 2), Minor.Population (column 6), and Education.Expenditures (C0lumn 7)
ed_exp1

ed_exp2 <- education[-c(1:9,22:50),-c(1,3:5)] # will give same results as ed_exp1 by ommitting raws and colums that we don't need (using negative vector)
ed_exp2

ed_exp3 <- education[which(education$Region == 2),names(education) %in% c("State","Minor.Population","Education.Expenditures")]
# We retrieve the columns of the subset by using the %in% operator on the names of the education data frame.
ed_exp3

ed_exp4 <- subset(education, Region == 2, select = c("State","Minor.Population","Education.Expenditures"))
# The subset() function returns subsets of vectors, matrices or data frames which meet conditions. Takes 3 arguments: the data frame you want subsetted, the rows corresponding to the condition by which you want it subsetted, and the columns you want returned. 
ed_exp4
```

For the last example in this article (using the `dplyr` package), use the `tidyverse` package you just installed instead. The `filter()` and `select()` functions are the same. Include the code from this article and your output as the first section of your markdown report.

```{r}
library(tidyverse)
ed_exp5 <- select(filter(education, Region == 2),c(State,Minor.Population:Education.Expenditures))
ed_exp5
```


### Part 3
**1. Create the `myClass` data frame we covered in class.** When you create the data frame, make sure that your character **strings** are not changed to **factors**. (look at `?data.frame` for the `stringsAsFactors` argument; also look at how the article does it). Include a row in the data frame for me, you, and your classmates. Here are the features to measure:
    a. last name
    b. first name
    c. number of cups of coffee or tea per day, and
    d. current neighbourhood
    
```{r}
myClass <- data.frame(
  LName = c("Odom", "Dyatchenko", "Ma", "Gmunder"),
  FName = c("Gabriel", "Nina", "Ruixan", "Kristin"),
  CofTeaCaps = c(0, 3, 2, 0),
  Neighb = c("Pembroke Pines", "Miami Beach", "Modera Riverhouse", "Brickell"),

stringsAsFactors = FALSE) # do not change strings to factors
```
    
    
**2. For each of the five data-frame subsetting methods in the article above, subset**
   
   ***i. Your row***
```{r}
myRaw1 <- myClass[2, c(1:4)]
myRaw1

myRaw2 <- myClass[-c(1,3,4), c(1:4)]
myRaw2

myRaw3 <- myClass[which(myClass$LName== "Dyatchenko"), names(myClass) %in% c("LName","FName","CofTeaCaps", "Neighb")]
myRaw3

myRaw4 <- subset(myClass, LName =="Dyatchenko", select = c(LName:Neighb)) # not each variable in quotes 
myRaw4

myRaw5 <- select(filter(myClass, LName == "Dyatchenko"), c(LName:Neighb)) # not each variable in quotes 
myRaw5
```
   ***ii. the column of neighbourhoods***
```{r}
Neighb1 <- myClass[, 4]
Neighb1

Neighb2 <- myClass[, -c(1:3)]
Neighb2


Neighb3 <- myClass[names(myClass) %in% c("Neighb")]
Neighb3

Neighb4 <- subset(myClass, select = c(Neighb)) # not each variable in quotes 
Neighb4

Neighb5 <- select(filter(myClass), c(Neighb)) # not each variable in quotes 
Neighb5
```
   
   ***iii. your current neighbourhood***
```{r}
myNeighb1 <- myClass[2, 4]
myNeighb1

myNeighb2 <- myClass[-c(1, 3:4), -c(1:3)]
myNeighb2

myNeighb3 <- myClass[which(myClass$LName== "Dyatchenko"), names(myClass) %in% c("Neighb")]
myNeighb3

myNeighb4 <- subset(myClass, LName=="Dyatchenko", select = c(Neighb))
myNeighb4

myNeighb5 <- select(filter(myClass, LName== "Dyatchenko"), c(Neighb))
myNeighb5
```
    ***iv. your AND my current neighbourhood, as a data frame***
```{r}
TwoNeighb1 <- myClass[1:2, 4]
TwoNeighb1

TwoNeighb2 <- myClass[-c(3:4), -c(1:3)]
TwoNeighb2

TwoNeighb3 <- myClass[which(myClass$LName %in% c("Odom", "Dyatchenko")), names(myClass) %in% c("Neighb")]
TwoNeighb3

TwoNeighb4 <- subset(myClass, LName %in% c("Odom", "Dyatchenko"), select = c(Neighb))
TwoNeighb4

TwoNeighb5 <- select(filter(myClass, LName %in% c("Odom", "Dyatchenko")), c(Neighb))
TwoNeighb5
```
    ***v. the rows with people who drink coffee or tea***
```{r}
head(myClass)
Drink1 <- myClass[2:3, 1:4]
Drink1

Drink2 <- myClass[-c(1,4), ]
Drink2

Drink3 <- myClass[which(myClass$LName %in% c("Dyatchenko", "Ma")), names(myClass) %in% c("LName","FName","CofTeaCaps", "Neighb")]
Drink3

Drink4 <- subset(myClass, LName %in% c("Dyatchenko", "Ma"), select = c(1:4)) # c(1:4) also worked
Drink4

Drink5 <- select(filter(myClass, LName %in% c("Dyatchenko", "Ma")), c(1:4))
Drink5
```
    ***vi. the neighbourhoods of people who *do not* drink coffee or tea***
```{r}
head(myClass)
NoDrink1 <- myClass[c(1,4), 1:4]
NoDrink1

NoDrink2 <- myClass[-c(2:3), ]
NoDrink2

NoDrink3 <- myClass[which(myClass$LName %in% c("Odom", "Gmunder")), names(myClass) %in% c("LName","FName","CofTeaCaps", "Neighb")]
NoDrink3

NoDrink4 <- subset(myClass, LName %in% c("Odom", "Gmunder"), select = c(1:4)) # c(1:4) also worked
NoDrink4

NoDrink5 <- select(filter(myClass, LName %in% c("Odom", "Gmunder")), c(1:4))
NoDrink5
```
