---
title: "Assignment 1"
author: "Nina Dyatchenko"
date: "September 3d, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Exercise set 1



1. Create an object called "myAge" that holds your age *in months*. Hint: the
   multiplication operator in R is "*".
   
```{r}
myAge <- 29 * 12 + 8
myAge
```


2. Using the object "myAge", approximate the number of days you've been alive.
   Use 30.44 days per month. Check this against your age in days on Wolfram
   Alpha. How many days off was your estimate?
   
```{r}
myAge * 30.44
# from Wolfram Alpha, I am 10827 days old today.
```

3. Using the object "myAge", find your decimal age. Hint: the division
   operator is "/".
   
```{r}
myAge / 12
```

4. Copy and Paste MyAge into the console and press ENTER. What happens? Why?
 
  Console returened error "Error: object 'MyAge' not found". Because R is case sencitive, it sees MyAge and myAge differently. myAge was defined in the code previously, but MyAge was not. Thus R gives the error. 




## Exercise set 2



1. Five people start the newest diet craze. Their weights (in kg) before and
   after were [78 72 78 79 105] and [67 65 79 70 93], respectively. Store
   these two vectors as "wtBefore" and "wtAfter", respectively. Find the total
   weight lost, the average weight lost, and the weight lost per person.
   
```{r}
wtBefore <- c(78, 72, 78, 79, 105)
wtAfter <- c(67, 65, 79, 70, 93)

# Total weight lost:
sum(wtBefore - wtAfter)

# Average weight lost:
mean(wtBefore - wtAfter)

# Weight lost per person:
wtBefore - wtAfter
```

   
2. Create the following vectors using the rep() and seq() functions:
   a) start with the first non-negative integer powers of 2
   
```{r}
2^(seq(from=0, to=8, by=1))
2^(0:8)
```

   b) 1, 1.5, 2, 2.5, ..., 12
   
```{r}
seq( from =1, to = 12 , by = 0.5)
```

   c) 1, 8, 27, 64, ..., 1000
   
```{r}
seq(from = 1, to = 10, by = 1)^3
```

   d) 1, -1/2, 1/3, -1/4, ..., -1/100
   
```{r}
library(MASS)
as.fractions(-(seq(from = -1, to = 1, by = 2)/seq(from = 1, to = 100, by = 1)))
```

```{r}
# or

-(seq(from = -1, to = 1, by = 2)/seq(from = 1, to = 100, by = 1))

```

   
   e) 1, 0, 3, 0, 5, 0, 7, 0, ..., 0, 49
   
```{r}

seq(from =1, to= 2, by=1)

```

   f) 1, 3, 6, 10, 15, ..., 210 (Hint: ?cumsum)
   
```{r}
cumsum(1:20)
```

   g) 1, 2, 2, 3, 3, 3, ..., 10, 10, 10, 10, 10, 10, 10, 10, 10, 10 (Hint: ?rep)
   
```{r}
x=1:10
rep(x, times = c(1:10), length.out = NA, each = 1)
```

   
3. (ADVANCED) The jth term of the Taylor-MacLaurin series for the natural
   logarithm is
   $$
   log(1 - x) := - \lim_{n \to \infty} \sum \limits_{j = 1}^n \frac{x ^ j}{j}.
   $$
   Find the residuals of this approximation for n = 5, 10, 50, 100 around x =
   0.25

```{r}
x=0.25
n=c(5, 10, 50, 100)
(x^(n+1))/(1-x)

```



## Exercise set 3


1. Create a vector of the months of the year and store it in an object called
   "mons".
   
```{r}
mons<- month.name
mons
```


2. You would like to discard the first three months, so you type "mons[-1:3]".
   What happened? Why should you type instead?
   
```{r}
# Error in mons[-1:3] : only 0's may be mixed with negative subscripts. R doesn't allow to #"knit" with the error

mons[1:3]

mons[4:12]
# or
mons[-(1:3)]

```

3. Find a method to use the "length()" function to find the last four entries
   of *any* atomic vector. Apply this to find the last four months of the
   year.
   
```{r}
mons[length(mons)-(3:0)]
```

4. Logically subset the uppercase vector of English letters in the following
   ways:
   a) Type LETTERS and press ENTER. What is your guess to find the lower case
      letters?

```{r}
LETTERS


letters

```

   b) Create a vector of the first 12 upper-case English letters
   
```{r}
LETT<- c(LETTERS[1:12])
LETT

```

   
   c) Create a vector of the 1st, 3rd, 5th, 7th, ..., 25th English letters
   
```{r}
LETTnum<- c(LETTERS[seq(from = 1, to = 26, by = 2)])
LETTnum

```

   d) Create a vector of the consonants. (Hint: it may be easier to find the
      letters that are *not* one of the vowels)
      
```{r}

```

      
